Figures to insert in text

### 2018-03-08 Chapters/Chapter02.tex
SDM

Our intention is to provide comparative performance metrics under different computation engines (CPU, GPU, etc) and different operating systems (Linux, MacOs, Windows, etc). Performance can be measured as the average number of scans of all hard locations per second, reads per second, writes per second, etc.

Our first device is a personal MacBook Pro Retina 13-inch Late 2013 with a 2.6GHz Intel core i5 processor, 6GB DDR3 RAM, and Intel Iris GPU.  We also intend to test on machines such as the iMac with dedicated GPU, MacPro with dedicated GPU, and personal computers under Linux with dedicated GPUs.

Beyond that, we are running as state-of-the-art devices: (i) an Amazon EC2 p3.xlarge with Intel Xeon E5-2686v4 processor, 61GB DDR3 RAM, and NVIDIA K80 GPU, and (ii) an Amazon EC2 p3.8xlarge with Intel Xeon E5-2686v4 processor, 488GB DDR3 RAM, and 8x NVIDIA K80 GPU.

>>>>

Performance is an important part of our framework. Running an SDM memory consumes a lot of resource from both CPU and RAM.

For instance, each scan in 1,000,000 hard-locations with 1,000 bits executes $10^9$ bit compares through $10^9/64 = 15,625,000$ XORs and calls to the built-in popcount. So, 10,000 writes execute $10^{13}$ bit compares, while a 6-iterative reading executes $6 \cdot 10^{12}$ bit compares. The heatmap of Figure \ref{fig:cir-dist-10k-writes-kanerva} executed $3.05 \cdot 10^{15}$ bit compares. For comparison, the number of seconds since Jesus's birth is 63,639,648,000 = $6.36 \cdot 10^{10}$. The number of people who have ever lived on earth is estimated to be $1,08 \cdot 10^{11}$. There are approximtely $1.8 \cdot 10^{9}$ websites in the internet.

Our first device is a personal MacBook Pro Retina 13-inch Late 2013 with a 2.6GHz Intel core i5 processor, 6GB DDR3 RAM, and Intel Iris GPU. Our second device is an iMac Retina 5K 27-inch 2017 with a 3.8GHz Intel core i5 processor, 8GB DDR4 RAM, and a Radeon Pro 580 8G CPU.

Beyond that, we are also running in state-of-the-art devices: (i) an Amazon EC2 p2.xlarge with Intel Xeon E5-2686v4 processor, 61GB DDR3 RAM, and NVIDIA K80 GPU, and (ii) an Amazon EC2 p3.2xlarge with Intel Xeon E5-2686v4 processor, 488GB DDR3 RAM, and NVIDIA Tesla V100 GPU.

Amazon EC2 p3.2xlarge has generated the heatmap of Figure \ref{fig:cir-dist-10k-writes-kanerva} in 15 minutes and 3 seconds. It has compared $3.37 \cdot 10^{12}$ bits per second through $52.6 \cdot 10^{9} = 52.6 \text{ billion}$ XORs and popcounts per second.

We have executed the same performance test in each device. The test has 3 parts. The first part consists of: 1,000 linear scans, 5,000 thread scans, and 5,000 OpenCL scans. The second part consists of 5,000 writes, 5,000 single reads, and 1,000 6-iterative readings, with both thread and opencl scanners. The code is available in the ``Performance test'' notebook \citep{sdmframework}.

\begin{figure}[!htb]
\centering\includegraphics[width=\textwidth]{images02/performance/imac-scans-1000.png}
\caption{Time to run a single scan in a SDM with $n=1,000$, $H=1,000,000$ and $r=451$.
\label{fig:performance-imac-scan-1000}}
\end{figure}

\begin{figure}[!htb]
\centering\includegraphics[width=\textwidth]{images02/performance/imac-scans-256.png}
\caption{Time to run a single scan in a SDM with $n=256$, $H=1,000,000$ and $r=103$.
\label{fig:performance-imac-scan-256}}
\end{figure}

\begin{figure}[!htb]
\centering\includegraphics[width=\textwidth]{images02/performance/imac-scans-10k.png}
\caption{Time to run a single scan in a SDM with $n=10,000$, $H=1,000,000$ and $r=4845$.
\label{fig:performance-imac-scan-10k}}
\end{figure}

\begin{center}
    iMac $n=1,000$ bits
    \begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 1000 & 81.62 & 12.25 \\
    Thread scan & 5000 & 143.68 & 6.95 \\
    OpenCL scan & 5000 & 238.00 & 4.20 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 1000 & 74.92 & 13.34 \\
    Thread single read & 1000 & 96.22 & 10.39 \\
    OpenCL write & 1000 & 126.50 & 7.90 \\
    OpenCL single read & 1000 & 190.20 & 5.25 \\
    \hline
    \end{tabular}
\end{center}

\begin{center}
    iMac $n=256$ bits
    \begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 1000 & 175.48 & 5.69 \\
    Thread scan & 5000 & 352.63 & 2.83 \\
    OpenCL scan & 5000 & 244.88 & 4.08 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 2000 & 304.46 & 3.28 \\
    Thread single read & 2000 & 391.21 & 2.55 \\
    OpenCL write & 2000 & 378.44 & 2.64 \\
    OpenCL single read & 2000 & 466.16 & 2.14 \\
    \hline
    \end{tabular}
\end{center}

\begin{center}
    iMac $n=10,000$ bits
    \begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
        Linear scan & 100 & 8.59 & 116.38 \\
        Thread scan & 500 & 18.66 & 53.56 \\
        OpenCL scan & 1000 & 77.20 & 12.95 \\
    \hline
    \end{tabular}
\end{center}
